---
title: "COVID-19-Cases-in-Toronto-in-different-Age-group"
categories: R
tags:
- R Markdown
- plot
- regression
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

# Part 1. Abstraction
we use @citetidyverse
After the COVID-19 outbreak happened, does everything fit with the current pathology? We need to find if there is any phenomenon that against pathology and we need to figure out why by analyze the data set which collected by Toronto Public Health.


# Part 2. Author Introduction
Name: Bowen Han
```{r,echo=FALSE,include=FALSE}
library(opendatatoronto)
library(dplyr)
library(tidyverse)

#1 get package
package <- show_package("64b54586-6180-4485-83eb-81e8fae3b8fe")

# get all resources for this package
resources <- list_package_resources("64b54586-6180-4485-83eb-81e8fae3b8fe")

# identify datastore resources; by default, Toronto Open Data sets datastore resource format to CSV for non-geospatial and GeoJSON for geospatial resources
datastore_resources <- filter(resources, tolower(format) %in% c('csv', 'geojson'))

# load the first datastore resource as a sample
data <- filter(datastore_resources, row_number()==1) %>% get_resource()

```

# Part 3. Data introduction

This data set is mainly about the COVID-19 cases in Toronto area and the source of data is managed by Toronto Public Health.

_id <int>: This variable is a unique row identifier for open data database.

Assigned_ID <int>: A unique identity that assigned to each cases to allowed tracking specific cases.

Outbreak Associated <chr>: Outbreak associated cases are associated with outbreaks of COVID-19 in Toronto healthcare institutions and healthcare settings and other Toronto congregate settings.

Age Group <chr>: Age group(≤19, 20-29, 30-39, 40-49, 50-59, 60-69, 70-79, 80-89, 90+, unknown)

Neighborhood Name <chr>: The name of geographically distinct neighborhood where the case located.

FSA <chr>: The first three postal code based on case's home address.

Source of Infection <chr>: The most likely way that sporadic cases get infected by COVID-19.(Travel,Close contact with a case,Institutional setting,Healthcare setting,Community,Pending ,Unknown/missing,N/A)

Classification <chr>: Categorize the cases as confirmed of probable.

Episode Date <chr>: The date that case get infected.

Reported Date <chr>: The date that case has been reported to Toronto Public Health.

Client Gender <chr>: Gender of cases.

Outcome <chr>: Fatal(Cases with a fatal outcome reported.), Resolved, Active(All other cases).

Currently in ICU <chr>: Cases that are currently admitted to the intensive care unit.

Currently Intubated <chr>: Cases that were intubated related to their COVID-19 infection.

Ever Hospitalized <chr>: Cases that were hospitalized related to their COVID-19 infection .

Ever in ICU <chr>: Cases that were admitted to the intensive care unit (ICU) related to their COVID-19 infection.

Ever Intubated <chr>: Cases that were intubated related to their COVID-19 infection.

# Part 4. Graph Simple

```{r, echo=FALSE}
# Creat a bar chart about the cases and age-group
ggplot(data, aes(x =`Age Group`, fill = `Age Group`)) + 
    geom_bar(stat = "count") +
    labs(title = "Total cases in each age group")
```


# Part 5. Discussion
According to the Bar chart we can see the most total cases happened in age group of 20-29 Years. Also, those middle-age(20-49) group have much higher total cases than children(19 and younger) and elders(50 and older).


# Part 6. Simple conclusion
After analyze the data set and graph, we can conclude that people who are between 20-49 years old are more likely infected by COVID-19. However, this phenomenon violates the pathology. As we all know, usually adults have much more stronger immune system compare with children and elders, which means adults should be the hardest age group to be infected.But the data never tells lie, especially when its size goes really  big. So there is a reason that may explain the conflict between the data set we got and the actual pathology. That is the COVID-19 need a media to spread, like air, and it can stay alive in air for a really long time.After the outbreak everyone had been told to avoid going out unnecessarily, children and elders start barricade themselves indoors but the bad new is someone must get out to get supplies for family.Therefore, the most stronger people in a family (usually between 20-49 years old)need to go out and buy daily stuffs in enclosed environment like supermarket and that will greatly increase the chance of infection.

# Part 7. Reference